Temporary Trade Barriers: \\ When Will They End?

### 2016-05-13 presentation.tex
add future work slide

\section{Overview}
\subsection{Preview}
\begin{frame}
\frametitle{P}
In 
\pause
\begin{itemize}[<+->]
	\item r
  \item g
	\item a
\end{itemize}
\end{frame}

@@

\begin{frame}{Outline of Talk}
\begin{enumerate}[<+->]
	\item B
	\item E
	\item R
	\item F
	\item Conclusion
\end{enumerate}
\end{frame}

@@

@@

\section{Conclusion}
\subsection{}
\begin{frame}{Future Work}
\begin{itemize}[<+->]
	\item C
	\item E
	\item P
	\item A
\end{itemize}
\end{frame}

\begin{frame}{Conclusion}
\begin{itemize}[<+->]
	\item S
	\item E
	\item F
\end{itemize}

>>>>

\section{Overview}
\subsection{Preview}
\begin{frame}
\frametitle{The Questions}
\pause
\begin{itemize}[<+->]
	\item How long do deviations from trade agreement tariffs last? 
  \item What are the determinants of these deviations?
		\begin{itemize}
			\item They don't happen for \textit{no} reason at all
			\item Take political economy perspective
		\end{itemize}
	\item 
\end{itemize}
\end{frame}

\begin{frame}{Institutional Detail}
\begin{enumerate}[<+->]
	\item Temporary trade barriers have potential to be renewed
		\begin{itemize}
			\item For Anti-dumping (AD) duties, initial five year term, renewal for five years
			\item For Safeguards, four then four; much rarer than AD
		\end{itemize}
	\item Authorized by WTO
	\item Very little in the agreements to guide the process
	\item WTO litigation has given governments a LOT of latitude on renewals
	\item Conclusion
\end{enumerate}
\end{frame}

@@

@@

\begin{frame}{What's this uncertainty about?}
\pause
Lobby must be able to trigger the original AD duty
\begin{itemize}
	\item \textit{Can} think of non-adherence to MFN as eqm path dispute
	\item It could be justified, not motivated by politics/rent-seeking
	\item But still, firms lobby for duties they don't get
\end{itemize}

\pause
\vskip.1in
So what's the uncertainty about?
\pause
\begin{itemize}[<+->]
	\item Strength of evidence
	\item Probability foreign will retaliate or initiate dispute (indirect)
	\item $G$'s valuation of harm to industry, e.g. how politically important is industry?
\end{itemize}

@@

\section{Conclusion}
\subsection{}
\begin{frame}{Future Work}
\pause
\begin{itemize}[<+->]
	\item Comparative static on uncertainty measure
	\item Empirical work
	\item Extend model to include initial decision to grant protection.
		\begin{itemize}
			\item Explain variation in a lobby's incentives between original application of AD and renewal
			\item Lobby's choice between investing in productive vs. rent-seeking behavior while protected
		\end{itemize}
\end{itemize}
\end{frame}

\begin{comment}
\begin{frame}{Conclusion}
\begin{itemize}[<+->]
	\item S
	\item E
	\item F
\end{itemize}

\end{frame}
\end{comment}
